---
title: "Handwritten Degits"
output:
  html_notebook:
    toc: yes
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
editor_options:
  chunk_output_type: inline
---

#Good Reference
http://rstudio-pubs-static.s3.amazonaws.com/6287_c079c40df6864b34808fa7ecb71d0f36.html

#Load Libraries
Ok...
There are quite a few (not going to use all I guess)!

```{r}
library("RColorBrewer")
library("ElemStatLearn")
library("foreign")
library("tree")
library("RWeka")
library("rpart")
library("maptree")
library("e1071")
library(tidyverse)
library(caret)
library(psych)
library(class)
### Set Color colorRampPalette(COLORS) ( 4 ) ## (n)
#CUSTOM_COLORS <- colorRampPalette(colors = COLORS)
#CUSTOM_COLORS_PLOT <- colorRampPalette(brewer.pal(10, "Set3"))
```

#Load Data
Since the data is quite big, let's take 1000 samples from the data set.
Strictly speaking, it is proffered to have the same probability to be chosen (1/10) but let's ignore this bit.
At the same time, Digit indicators are created (there is a better way).

```{r}
Train.df <- read.csv("C:/Users/key_a/Desktop/Digit Recognizer/train.csv",
                     #file.choose(),
                     header = T) %>% 
  sample_n(., 2000) %>% 
  mutate(label = factor(label))
Train.df2 <- Train.df %>%
  mutate(Digit0 = if_else(label == 0, 1, 0),
         Digit1 = if_else(label == 1, 1, 0),
         Digit2 = if_else(label == 2, 1, 0),
         Digit3 = if_else(label == 3, 1, 0),
         Digit4 = if_else(label == 4, 1, 0),
         Digit5 = if_else(label == 5, 1, 0),
         Digit6 = if_else(label == 6, 1, 0),
         Digit7 = if_else(label == 7, 1, 0),
         Digit8 = if_else(label == 8, 1, 0),
         Digit9 = if_else(label == 9, 1, 0))
dim(Train.df)
head(Train.df)
```

#Exploratory analysis
We didn't really cover this in the previous sessions but it is always good to explore what we have!

##Summary Check
```{r echo = T}
summary(Train.df)
```

##Missing Value Check
Remember, data is messy in the real world!

```{r}
sum(is.na(Train.df))
```



#Plot
Any bias in the data?

```{r}
barplot(table(Train.df$label))
```

Seems fine!
There are about the same number of digits.

#Model
Logistic for... 3?

```{r}
Train.glm <- glm(Digit3 ~ ., family = "binomial", maxit = 25, data = Train.df2 %>% select(Digit3, starts_with("pixel")))
summary(Train.glm)
Train.df2Pred = Train.df2 %>% select(Digit3, starts_with("pixel")) %>%
  mutate(Prediction3 = if_else(predict(Train.glm, type = "response")>0.5,1,0))
head(Train.df2Pred)
table(Actual = Train.df2Pred$Digit3 ,Pred = Train.df2Pred$Prediction3)
```

The hard part of modeling handwritten character/digits is strong correlation between independent variables.

```{r}
#par(mfrow = c(4, 4), pty = "s", mar = c(3, 3, 3, 3), xaxt = "n", yaxt = "n")
for (i in 1:10) {
    z <- array(as.vector(as.matrix(Train.df[i, -1])), dim = c(28, 28))
    z <- z[, 28:1]  ##right side up
    image(1:28, 1:28, z, main = Train.df[i, 1])
    print(i)
}
```


#Regression Tree
```{r}
model.rpart <- rpart(  ~ ., method = "class", data = Train.df)
printcp(model.rpart)
draw.tree(model.rpart, cex = 0.5, nodeinfo = TRUE, col = gray(0:8/8))
```

##Rpart Prediction
Let's predict (with train dataset), and see how computer get confused.

```{r}
Train.dfRPart = cbind(Train.df, Prediction = predict(model.rpart, type = 'class'))
table(Train.dfRPart$label, Train.dfRPart$Prediction)
Train.dfRPart[Train.dfRPart$label != Train.dfRPart$Prediction,][1:10, c(1,length(Train.dfRPart))]
for (i in 1:10) {
    z <- array(as.vector(as.numeric(as.matrix(Train.dfRPart[Train.dfRPart$label != Train.dfRPart$Prediction,][i, -1]))), dim = c(28, 28))
    z <- z[, 28:1]  ##right side up
    image(1:28, 1:28, z, main = Train.dfRPart[Train.dfRPart$label != Train.dfRPart$Prediction,][i, 1])
    print(i)
}
```

#Classification. k-Nearest Neighbors (kNN) Algorithm

```{r}
repeats = 3
numbers = 10
tunel = 10

set.seed(1234)
x = trainControl(method = "repeatedcv",
                 number = numbers,
                 repeats = repeats,
                 classProbs = TRUE,
                 summaryFunction = twoClassSummary)
train(label ~ ., data = Train.df, method = "knn",
               preProcess = c("center","scale"),
               trControl = x,
               metric = “ROC”,
               tuneLength = tunel)

?knn()
knn(label ~ ., train = Train.df, test = Train.df, cl = Train.df$label, k = 10)
```

